Towards Artificial Intelligence for Metaphysics: \\ the Case of the Inconsistency in G\"odel's Ontological Argument

### 2016-01-07 Papers/InProgress/IJCAI/paper.tex
Write section about embeddings and embedding of S5+

For a computational analysis of G\"odel's ontological argument in this
approach the embedding of modal higher-order logics (MHOL) such as K,
KB and S5 for different domain conditions (possibilist and actualist)
is required. This idea has been successfully followed in related work
\cite{C40}. The embedding of modal higher-order logic is in fact
straightforward. Formulas in MHOL such as are lifted to predicates
over worlds, which are explicitly represented in the approach as
terms. Propositional MHOL such as $\neg \varphi$, $\varphi\vee\psi$
and $\box \varphi$ are then mapped to HOL formulas \ldots.

It is easy
to see that this captures the standard translation \cite{Ohlbach},
which is here (intra-logically) realised in HOL by stating a set of
equations; see also Fig. ~\ref{QMLS5}. New is that also quantifiers 
can be mapped \ldots

The approach is very flexible, KB, S5, domain conditions\ldots

\subsection{Improved Embedding for S5}
We present an improved embedding (syntax and defintion of box) in  Fig.~\ref{QMLS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/QMLS5.png}}
\caption{Improved Embedding of S5} \label{QMLS5}
\end{figure}

@@

\subsection{Mapping to Gödel's Script}
\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/Manuscript2.png}}
\caption{Sources of Inconsistence in G\"{o}del's proof script.} \label{GoedelScript}
\end{figure*}

>>>>

For a computational analysis of G\"odel's ontological argument in this
approach the embedding of higher-order modal logics (HOML) such as K,
KB and S5 with various domain conditions (possibilist and actualist)
is required. This idea has been successfully followed in related work
\cite{C40}. The embedding of higher-order modal logic is in fact
straightforward. Formulas in HMOL are \emph{lifted}, translated to predicates
over worlds, which are themselves explicitly represented as
terms. The logical constants of HMOL are translated to HOL terms in such a way that, for instance, 
%$\neg \varphi$, $\varphi\vee\psi$
$\Box \varphi$ and $\Diamond \varphi$ are mapped, respectively, to the HOL formulas $\forall w. (r w_0 w) \imp (\varphi w)$ and $\exists w. (r w_0 w) \wedge (\varphi w)$. This form of embedding is precisely the well-known standard translation \cite{Ohlbach,ModalLogicPatrickBlackburn},
which is here (intra-logically) realized in HOL by stating a set of
equations defining the logical constants (Fig. ~\ref{QMLS5}). The resulting object logic is the HOML K with rigid terms and constant domains (possibilist quantifiers). Other logics (e.g. KB, S5) can be embedded by adding axioms that restrict the accessibility relation $r$. Varying domains and actualist quantifiers can be simulated by means of an existence predicate, which can be used to guard the quantifiers. Therefore, the embedding approach is very flexible.

\subsection{Improved Embedding for S5+}

The modal logic S5 requires that the accessibility relation be reflexive, symmetric and transitive. The usual approach to embed S5 would be to use the standard translation for K described above and state these additional conditions as three HOL axioms: 
\begin{itemize}
\item Reflexivity: $\forall x. (r~x~x)$
\item Symmetry: $\forall x. \forall y. (r~x~y) \rightarrow (r~y~x)$ 
\item Transitivity: $\forall x. \forall y, \forall z. (r~x~y) \wedge (r~y~z) \rightarrow (r~x~z)$
\end{itemize}

We consider here a modal logic that we call S5+, which is characterized by the following condition on the accessibility relation:
\begin{itemize}
\item Omni-accessibility: $\forall x. \forall y. (r~x~y)$
\end{itemize}

It is easy to see that S5+ is at least as strong as S5: omni-accessibility entails reflexivity, symmetry and transitivity. S5+, in fact, \emph{strictly stronger} than S5. S5+ only admits complete\footnote{\emph{Complete} in the graph-theoretical sense: for any directed pair of vertices/worlds there is a directed edge connecting them.}} frames, whereas S5 admits non-complete frames as long as all their components are complete.

For S5+, an improved embedding is possible. Omni-accessibility implies that the guarding predicates in the definitions of $\Box$ and $\Diamond$ always hold. Therefore, they can be omitted, and the modal operators can be defined instead merely as:
\begin{itemize}
\item $\Box \varphi \equiv \forall w. (\varphi w)$ 
\item $\Diamond \varphi \equiv \exists w. (\varphi w)$
\end{itemize}

This improved embedding for S5+ is shown in Fig.~\ref{QMLS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/QMLS5.png}}
\caption{Improved Embedding of S5} \label{QMLS5}
\end{figure}

\section{Adequacy of S5+ for Metaphysics}

S5+ is only slightly stronger than S5.  ToDo

@@
